microscopy Data Clean

### 2020-07-29 Microscopy Data Clean.Rmd
added t-test for mixed aggregates

```
#Mixed Aggregates Analysis
```{r mixed aggregates import data} 
ReadMixedAggregateFile<-function(sample, imageSource){#This function outputs total number of pixels in the csv file from matlab
  file<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/MixedAggregates/', sample,imageSource, '.csv')
  datos <-read.csv(file, header = TRUE)
  colnames(datos)<-c('Size', 'Sa', 'Pa', 'Overlap', 'Slice')
  datos<-datos %>% mutate(Sample = sample)
  return(datos)
}
testReadMixedAggregateFile<-ReadMixedAggregateFile('5-8-19','RedSubtract')
PA14mut<- c('4-24-19', '4-25-19', '5-8-19')
#wt data retrieval
mixedAggDataWtList<-map2(PA14wt,'RedSubtract', ReadMixedAggregateFile) 
mixedAggDataWt<-bind_rows(mixedAggDataWtList)
mixedAggDataWt<-mixedAggDataWt %>% mutate(Strain = "PA14wt")
#mut data retrieval
mixedAggDataMutList<-map2(PA14mut,'RedSubtract',ReadMixedAggregateFile) 
mixedAggDataMut<-bind_rows(mixedAggDataMutList)
mixedAggDataMut<-mixedAggDataMut %>% mutate(Strain = "PA14mut")

@@

>>>>

```
#Mixed Aggregates Analysis
```{r mixed aggregates import data} 
ReadMixedAggregateFile<-function(sample, imageSource){#This function outputs total number of pixels in the csv file from matlab
  file<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/MixedAggregates/', sample,imageSource, '.csv')
  datos <-read.csv(file, header = TRUE)
  colnames(datos)<-c('Size', 'Sa', 'Pa', 'Overlap', 'Slice')
  datos<-datos %>% mutate(Sample = sample)
  return(datos)
}

PA14mut<- c('4-24-19', '4-25-19', '5-8-19')
#wt data retrieval
mixedAggDataWtList<-map2(PA14wt,'RedSubtract', ReadMixedAggregateFile) 
mixedAggDataWt<-bind_rows(mixedAggDataWtList)
mixedAggDataWt<-mixedAggDataWt %>% mutate(Strain = "PA14wt")
#mut data retrieval
mixedAggDataMutList<-map2(PA14mut,'RedSubtract',ReadMixedAggregateFile) 
mixedAggDataMut<-bind_rows(mixedAggDataMutList)
mixedAggDataMut<-mixedAggDataMut %>% mutate(Strain = "PA14mut")

@@

#T-tests

tTestMixWt<-combinedMixedAggData %>% filter(Strain == "PA14wt") %>% pull(PercentTotalBiomass)
tTestMixMut<-combinedMixedAggData %>% filter(Strain == "PA14mut") %>% pull(PercentTotalBiomass)
tTestMixAggs<-t.test(x = tTestMixWt, y = tTestMixMut, paired = F)
